Data Preparation

### 2019-01-09 Data Preparation.Rmd
Including newly created variables to the course dataset

>>>>

```{r}
d_course <- d_course %>%
  full_join(d_ILO_detail       , by = "Code") %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code") %>%
  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
print(d_course)
```
